A comparative study of batch construction strategies \\ for recurrent neural networks in MXNet

### 2017-04-19 paper/paper.tex
add Pavel

\makeatletter
\def\name#1{\gdef\@name{#1\\}}
\makeatother \name{{\em Patrick Doetsch, Hermann Ney}}

\address{Human Language Technology and Pattern Recognition,
 Computer Science Department, \\
 RWTH Aachen University, 52062 Aachen, Germany \\
  {\small \tt \{doetsch,ney\}@cs.rwth-aachen.de}
}

>>>>

\makeatletter
\def\name#1{\gdef\@name{#1\\}}
\makeatother \name{{\em Patrick Doetsch, Pavel Golik, Hermann Ney}}

\address{Human Language Technology and Pattern Recognition,
 Computer Science Department, \\
 RWTH Aachen University, 52062 Aachen, Germany \\
  {\small \tt \{doetsch,golik,ney\}@cs.rwth-aachen.de}
}
